Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-19 Answers_for_reviewers.tex

\title{Answers for the Reviewers  for the paper "Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes"}

\author{Emmanuel Franck\footnotemark[1] \footnotemark[2],
C. Buet \footnotemark[3], 
B. Despr\'es\footnotemark[4], 
T. Leroy\footnotemark[4] \footnotemark[3]
}
 \footnotetext[1]{INRIA Nancy Grand-Est & IRMA Strasbourg}
 \footnotetext[3]{CEA, DAM, DIF, F-91297 Arpajon Cedex,France}
 \footnotetext[4]{Laboratoire Jacques-Louis Lions,
  Universit\'e Pierre et Marie Curie,
  75252 Paris Cedex 05,
  France}
\footnotetext[2]{Email adress: emmanuel.franck@inria.fr}

\maketitle

\section{Answers for the report 2M}
\begin{itemize}
\item Comments and suggestions
\begin{itemize}
\item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
\item 3: We have added a sentence to explain why we use this formulation of the scheme and not the classical Gosse-Toscani scheme. For the remark about " the authors choose to renounce to the well- balanced property of the original 1D Gosse-Toscani scheme (except on uniform Cartesian grids) while retaining only its AP character" it is not clear that we say that. Indeed the scheme is well balanced for a subset of steady states (see annex of the paper "design of AP scheme ..."): the steady state associated to $u=Cts$ and $p$ linear. This property is perhaps impotent for the uniform convergence. At the end we renounce only to the steady states associated to $\nabla{u}=\nabla\times \phi$ with $\phi$ a potential. 
\item 4: We have correct this part introducing $v$ to obtain a not confusing proof.
\item 5: We have replaced is $\mathbf{u}^{\eps}$ by $u^{\eps}$
\item 6 : We have replaced the proposition 2.8 by the Lemma 2.8
\item 7 : We have added the reference on the paper "Time asymptotic high order ..." at the end of the 2D in the numerical results.
\item 8 : We have corrected the proposition 
\item 9 : We have added the missing "("
\end{itemize}
\item Minor issues and Typos
\begin{itemize}
\item 1: We have replaced $P^0$ by "first order"
\item 2 : we have corrected this sentence 
\item 3 : we have corrected this sentence 
\item 4 : we have corrected this sentence. (17) correspond to the scheme not the smooth data.
\item 5 : we have corrected this sentence. 
\item 6 : we have corrected your two remarks in this page 
\item 7 : we have corrected this sentence. 
\item 8: We have replaced $\gamma$ by $\tau$ in the numeric part.
\item 9: The date for the L. Gosse paper have been modified. for the S. Jin article we have copy the reference written on the website of S. Jin 
\end{itemize}
\end{itemize}
\end{document}

### 2015-03-19 Corrected_version.tex
last corrections

The natural cellwise initialization is chosen
\begin{equation} \label{eq:initp1}
p_j^\eps(0)=p_0(x_j) \mbox{ and }
u_j^\eps(0)=-\frac\eps\sigma \partial_x p_0(x_j) \mbox{ for all }j\in \mathbb Z.
Our goal is this section is to show that this scheme is AP.

>>>>

  We use another formulation of the Gosse-Toscani obtained using the Jin-Levemore scheme \cite{jinlev} and a discretization of the source term which use the fluxes. Contrary to the Gosse-Toscani scheme which use Riemann problem, this formulation based a basic algebraic computation is easier to write in 2D on unstructured meshes (the design is detailed in \cite{glaceap}).

The natural cellwise initialization is chosen
\begin{equation} \label{eq:initp1}
p_j^\eps(0)=p_0(x_j) \mbox{ and }
u_j^\eps(0)=-\frac\eps\sigma \partial_x p_0(x_j) \mbox{ for all }j\in \mathbb Z.
\end{equation}
Our goal is this section is to show that this scheme is AP.
